The \project{unRAVE} catalog

### 2016-08-18 article/unrave.tex
Minor

We chose to adopt a data-driven model --- rather than a physics-driven model ---
for this analysis.  Specifically we will use an implementation of \thecannon\
\citep{Ness_2015}.  Although this choice complicated the construction of our model
(e.g., see Section \ref{sec:the-training-set}), a data-driven model makes
use of all available information in the spectrum, and lowers the S/N ratio at
which systematic effects begin to dominate.  In other words, a well-constructed
data-driven model will yield more precise labels (e.g., stellar parameters and
chemical abundances) at low S/N ratios than most physics-driven models\footnote{
However, see \citet{Casey_2016}}.  This is particularly relevant for the 
low-resolution \rave\ data analysed here, because about half of the spectra have
S/N $\lesssim 50$.

Throughout this work we adopt the assumptions and nomenclature as set out in
\citet{Casey_2016}.  One distinction here is that the \emph{labelled} set and
the \emph{training} set in this work will be the same set.  In \citet{Casey_2016}
the labelled set contained two sub-sets: the training set and a distinct
validation set, allowing us to train on the \emph{training set} and then test
on the \emph{validation set}, a subset of the labelled set.  However in this work
the labelled set is relatively small, about an order of magnitude smaller than 
what was available in \citet{Casey_2016}, and therefore we will use all labelled 
set stars in the training step and supplement our validation experiments with 
literature comparisons.  Thus, throughout this work we will use the terms 
\emph{labelled set} and \emph{training set} interchangeably.  Below we describe 
how the training set was constructed before outlining the model we adopt.

@@

\bibitem[Casey et al.(2016)]{Casey_2016} Casey, A.~R., Hogg, D.~W., Ness, M., et al.\ 2016, arXiv:1603.03040

@@

>>>>

We chose to adopt a data-driven model --- rather than a physics-driven model ---
for this analysis.  Specifically we will use an implementation of \thecannon\
\citep{Ness_2015,Ness_2016}.  Although this choice complicated the construction 
of our model (e.g., see Section \ref{sec:the-training-set}), a data-driven model 
makes use of all available information in the spectrum, and lowers the S/N ratio 
at which systematic effects begin to dominate.  In other words, a well-constructed
data-driven model will yield more precise labels (e.g., stellar parameters and
chemical abundances) at low S/N ratios than most physics-driven models\footnote{
However, see \citet{Casey_2016a}}.  This is particularly relevant for the 
low-resolution \rave\ data analysed here, because about half of the spectra have
S/N $\lesssim 50$.

Throughout this work we adopt the assumptions and nomenclature as set out in
\citet{Casey_2016b}.  One distinction here is that the \emph{labelled} set and
the \emph{training} set in this work will be the same set.  In \citet{Casey_2016b}
the labelled set contained two subsets: the training set and a distinct
validation set, allowing us to train on the \emph{training set} and then test
on the \emph{validation set}, a subset of the labelled set.  However in this work
the labelled set is relatively small, about an order of magnitude smaller than 
what was available in \citet{Casey_2016b}, and therefore we will use all labelled 
set stars in the training step and supplement our validation experiments with 
literature comparisons.  Thus, throughout this work we will use the terms 
\emph{labelled set} and \emph{training set} interchangeably.  Below we describe 
how we constructed the training set, before we outline the model that we adopt.

@@

\bibitem[Casey(2016)]{Casey_2016a} Casey, A.~R.\ 2016, \apjs, 223, 8

\bibitem[Casey et al.(2016)]{Casey_2016b} Casey, A.~R., Hogg, D.~W., Ness, M., et al.\ 2016, arXiv:1603.03040

@@

\bibitem[Ness et al.(2016)]{Ness_2016} Ness, M., Hogg, D.~W., Rix, H.-W., et al.\ 2016, \apj, 823, 114
